Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-20 Markdown Documents/Manuscript.Rmd
Another paragraph down

National parks undeniably represent a critical infrastructure for supporting ecological integrity and outdoor recreation in the United States, but have recently drawn public attention for considerable underfunding [@simmonds_crisis_2018;@duncan_opinion_2016]. Most noteably for the $12 billion repair backlog for basic maintence and resource protection [@nps_nps_2018]. In additiion to necessary repairs, the National Park Service reports a 14% reduction in staff funding over the last 5 years [@doi_fiscal_2019]. While the majority of National Park Service funding comes from congressional appropriations, recent bugetary restrictions have put pressure on parks to gather an increasing amount of their budget from recreational visitor fees such as admissions and camping.  The income from these fees has been steadily increasing over the last 10 years as parks have seen visitation increases while simultanously increasing visitor fees [@gao_national_2016].

>>>>

National parks undeniably represent a critical infrastructure for supporting ecological integrity and outdoor recreation in the United States, but have recently drawn public attention for considerable under funding [@simmonds_crisis_2018;@duncan_opinion_2016]. Most notably for the $12 billion repair backlog for basic maintenance and resource protection [@nps_nps_2018]. In addition to necessary repairs, the National Park Service reports a 14% reduction in staff funding over the last 5 years [@doi_fiscal_2019]. While the majority of National Park Service funding comes from congressional appropriations, recent budgetary restrictions have put pressure on parks to gather an increasing amount of their budget from recreational visitor fees such as admissions and camping.  The income from these fees has been steadily increasing over the last 10 years as parks have seen visitation increases while simultaneously increasing visitor fees [@gao_national_2016].

As national parks become increasingly dependent on visitor fees in order to provide the suite of social and ecological services communities depend on, it is of paralleled importance to understand the drivers of fluctuation in recreational visits. Research has shown that economic considerations (e.g. park fees) are considerably less influential on park visitation than are recreational opportunities [@neuvonen_visits_2010;@stevens_declining_2014]. Most factors which influence the recreational accessibility of a given park are either fixed (natural resources within the park area) or within the control of park management (permitting, trail building, etc.). Wildfire smoke however, shows considerable yearly variation and is largely produced by adjacent public lands and therefore out of the jurisdiction of park management [@dombeck_wildfire_2004;@collins_regional_2006].
